\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[official]{eurosym}

\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[hidelinks]{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\fancyfootoffset[R]{0in}
% \rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\bibliographystyle{unsrt}
\nobibliography{mypublicationssimple}

{\Large \scshape Curriculum Vitae} \\
\small
\section{Personal Information}

\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}l}
  \textbf{Full Name:} & Seongmin Lee \\
  \textbf{Full Curriculum Vitae:} & \href{https://nimgnoeseel.github.io/resources/cv/cv.pdf}{\underline{https://nimgnoeseel.github.io/resources/cv/cv.pdf}} \\
  \textbf{Google Scholar:} & \href{https://scholar.google.com/citations?user=-YSnc6kAAAAJ&hl=en}{\underline{https://scholar.google.com/citations?user=-YSnc6kAAAAJ\&hl=en}} \\
  \textbf{Personal Website:} & \href{https://nimgnoeseel.github.io}{\underline{https://nimgnoeseel.github.io}} \\
\end{tabular*}

\section{Research Interests}

My research interest lies in software testing and program analysis. The overarching objective of my research is \textbf{achieving practical software testing in real-world scenarios} by addressing the challenges associated with the scale and complexity of software systems, overcoming the limitations of formal methods, and taking account of the operational behavior of software systems. I \textbf{utilize statistical methods to analyze dynamic information from program execution}, facilitating the reasoning of a program's semantic properties and addressing empirical challenges in software testing.

\section{Education and Employment}
\resumeSubHeadingListStart
\vspace{-2pt}
\item Max Planck Institute for Security and Privacy \hfill Germany \vspace{-2pt}
\vspace{-2pt} \item \hspace{10pt} \textbf{Postdoctoral Researcher, Software Security Research group} (Group head: Dr. Marcel Böhme) \hfill  Sep. 2022 -- Present

\vspace{-2pt}
\item Korea Advanced Institute of Science and Technology \hfill Republic of Korea \vspace{-2pt}
\vspace{-2pt} \item \hspace{10pt} \textbf{Doctor of Philosophy, School of Computing} (Advisor: Dr. Shin Yoo) \hfill  Sep. 2016 -- Aug. 2022

\vspace{-2pt} \item \hspace{10pt} \textbf{Bachelor of Science, School of Computing} \hfill  Feb. 2012 -- Aug. 2016
\vspace{-5pt} \item \hspace{10pt} \textbf{Bachelor of Science, Department of Mathematical Sciences}
\resumeSubHeadingListEnd

\section{Selected Publications \scriptsize{(* J: Journal, C: Conference)}}

% \textbf{Journal Articles}\vspace{-4pt}

\begin{itemize}
  \item[\textbf{J1}] \bibentry{leeCausalProgramDependence2025}
  \item[\textbf{C1}] \bibentry{leeChaomi2024}
  \item[\textbf{C2}] \bibentry{liyanageExtrapolatingCoverageRate2024}
        (*\emph{Co-first authors with equal contribution})
  \item[\textbf{C3}] \bibentry{leeStatisticalReachabilityAnalysis2023}
  \item[\textbf{C4}] \bibentry{ohEffectivelySamplingHigher2021}
  \item[\textbf{J2}] \bibentry{leeObservationbasedApproximateDependency2021}
  % \item[\textbf{J3}] \bibentry{leeEvaluatingLexicalApproximation2020}
  % \item[\textbf{C5}] \bibentry{leeClassifyingFalsePositive2019a}
\end{itemize}


\section{Academic Services \scriptsize{(* Services before 2023 are omitted.)}}
\begin{itemize}
  \item Program committee: ASE'24, ISSTA'24, FUZZING'24, SCAM'24, ASE'23
  \item Reviewer: TOSEM'24, TSE'24, IST'24, ASE'24
\end{itemize}


\section{Grants and Fellowships}
\begin{itemize}
  \item Title: \emph{Statistical Security Analysis for Large, Evolving Software} \\
        Grant ID: DFG under Germany's Excellence Strategy - \textbf{EXC 2092 CASA - 390781972} \\
        Amount: Salary according to the remuneration group E 14 TV-L (full time, $\sim$ \euro{136,000}), Duration: 2024.01.01 -- 2025.12.31
\end{itemize}


\section{Awards and honors}
\begin{itemize}
  \item \textbf{Distinguished Artifact Reviewer Award}, 33rd USENIX Security Symposium, 2024
  \item \textbf{PhD Dissertation Award}, School of Computing, KAIST, 2022
        \vspace{-5pt}\begin{itemize}
          \item \emph{Title of Dissertation: Statistical Program Dependence Approximation}
        \end{itemize}
  \item \textbf{2021 Naver Ph.D. Fellowship Award}: Awarded by NAVER Corp. to Ph.D. candidates who have published an outstanding research paper or have excellent publication performance, 2021
\end{itemize}

\end{document}